\thetitle

### 2013-04-13 tfpie/tfpie.tex
down with ()

class Examples {
    void test_tree(Tester t) {
        t.checkExpect((new Leaf(7)).sum(), 7);
        t.checkExpect((new Node(new Leaf(1),
                                5, 
                                new Node(new Leaf(0), 10, new Leaf(0)))).sum(),
                      16);
    }
}
\end{verbatim}
\caption{Binary tree sum in How to Design Classes}
\end{figure}

>>>>

class Examples {
    void test_tree(Tester t) {
        t.checkExpect(new Leaf(7).sum(), 7);
        t.checkExpect(new Node(new Leaf(1),
                               5, 
                               new Node(new Leaf(0), 10, new Leaf(0))).sum(),
                      16);
    }
}
\end{verbatim}
\caption{Binary tree sum in How to Design Classes}
\end{figure}
